A Switching Planner for Combined Task and Observation Planning

### 2010-11-24 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
MOre small fixes

@@

Our approach uses sequential planning to compute a linear plan, and
one trace of that plan's execution. The latter encapsulates
assumptions about: (1) the true underlying state, (2) how the plan's
execution will progress, and (3) the possibility of the agent
eventually holding strong beliefs about the truth values of specific
state propositions. Sequential planning proceeds in a continual manner
until the verification of an assumption about a runtime state
proposition is scheduled. At that point the system switches to a
decision-theoretic planner that is used to tailor sensory processing
by the robot to test the validity of the assumptions made so far.

@@

\[
\begin{array}{l}
s_0 \equiv \{(=(\pp{is-in}~\pp{DORA})~\pp{kitchen}),\\
\;\;(=(\pp{is-in}~\pp{box})~\#), (=(\pp{is-in}~\pp{cup})~\#)\}.
\end{array}
\]

@@

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$ in $\bstate_0$, then before it is executed blindly,
the sequential continual planning switches to a decision-theoretic
session, discussed in detail below. Overall, by scheduling $\action$
the sequential planner makes a naive assumption about the possibility
of the agent eventually ``committing'' to the truth values of specific
state propositions in $\poss{\action}$. The role of decision-theoretic
plans is to examine the validity of assumptions about the runtime
state of sequential planning. Second, if the truth value of $\prop$ is
not known, and no assumption is made about it in the current abstract
state, then if $\prop \in
\poss(\action)$ we have that action $\action$ is not applicable.

@@

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. In other words, writing $V_i$ for
the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
s_1, a_1,.., s_N$, we have

\[
V^* = \arg\min_{V_i} \Expect \bigg{[} 
\sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{PLAN}_t) \mid \pp{PLAN}, \bstate_0
\bigg{]} - V_i.
\]

In goal directed problems, where the only non-zero reward is received
at the first transition to a goal state, the Eq~\ref{eq:tracevalue}
criteria corresponds exactly to that of
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy. Finally, it is
worth clarifying that although the above discussion has been in terms
of a trace of length $N$, there is nothing in our approach that
artificially limits the length of candidate sequential plans.

>>>>

Sequential planning proceeds in a continual manner until the
verification of an assumption about runtime state is scheduled. At
that point the system switches to a decision-theoretic planner that is
used to tailor sensory processing by the robot to test the validity of
the assumptions made so far.

@@

Our approach uses sequential planning to compute a linear plan, and
one trace of that plan's execution. The latter encapsulates
assumptions about: (1) the true underlying state, (2) how the plan's
execution will progress, and (3) the possibility of the agent
eventually holding strong beliefs about the truth values of specific
state propositions.

@@

\[
\begin{array}{l}
\state_0 \equiv \{(=(\pp{is-in}~\pp{DORA})~\pp{kitchen}),\\
\;\;(=(\pp{is-in}~\pp{box})~\#), (=(\pp{is-in}~\pp{cup})~\#)\}.
\end{array}
\]

@@

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$ in $\bstate_0$, then before it is executed blindly,
the sequential continual planning switches to a decision-theoretic
session, discussed in detail below. Overall, by scheduling $\action$
the sequential planner makes a naive assumption about the possibility
of the agent eventually ``committing'' to the truth values of specific
state propositions in $\poss(\action)$. The role of decision-theoretic
plans is to examine the validity of assumptions about the runtime
state of sequential planning. Second, if in the current state \state\
the value of $\prop$ is $\#$ ---because a truth value is not specified
in $\state_0$ and no assumption is made about it in the plan
to \state--- then if $\prop \in \poss(\action)$, or if $\prop$ is the
subject of a positive or negative effect of $\action$, we have that
action $\action$ is not applicable in \state.

@@

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. %% In other words, writing $V_i$ for
%% the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
%% s_1, a_1,.., s_N$, we have
%%
%% \[
%% V^* = \arg\min_{V_i} \Expect \bigg{[} 
%% \sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{PLAN}_t) \mid \pp{PLAN}, \bstate_0
%% \bigg{]} - V_i.
%% \]
%%
In goal directed problems, where the only non-zero reward is received
at the first transition to a goal state, the Eq~\ref{eq:tracevalue}
criteria corresponds exactly to that of
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy. Finally, it is
worth clarifying that although the above discussion has been in terms
of a trace of length $N$, there is nothing in our approach that
artificially limits the length of candidate sequential plans.
